---
title: "Intelligent Feature Selection for DIMV"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Intelligent Feature Selection for DIMV}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

## Overview

The `dimvR` package provides optional feature selection for DIMV imputation.
This can reduce noise and multicollinearity in conditional regressions.

Available methods:

- `adaptive`: median-based correlation threshold
- `fixed`: fixed correlation threshold
- `mi`: mutual information (histogram-based)
- `hybrid`: combined correlation and MI

## Basic usage

```{r}
library(dimvR)
set.seed(123)

X <- data.frame(
  x1 = rnorm(100),
  x2 = rnorm(100),
  x3 = rnorm(100),
  x4 = rnorm(100)
)

X$x2 <- 0.9 * X$x1 + rnorm(100, sd = 0.2)
X$x3 <- 0.6 * X$x1 + rnorm(100, sd = 0.3)

res_adaptive <- select_features_adaptive(X, target_var = "x1", method = "adaptive")
res_fixed <- select_features_adaptive(X, target_var = "x1", method = "fixed", threshold = 0.4)
res_mi <- select_features_adaptive(X, target_var = "x1", method = "mi")
res_hybrid <- select_features_adaptive(X, target_var = "x1", method = "hybrid")

res_adaptive$selected_names
```

## Integration with DIMV

```{r}
imp <- dimv_train(X, lambda = 0.1, feature_select = TRUE)
print(imp)
```

## Notes

- Feature selection is currently experimental and may change.
- MI is a simple histogram-based estimator for speed and portability.
